### 2024-09-02 manuscript.tex
Improve figure caption

\begin{figure}
\centering
\includegraphics[width=\textwidth]{img/cl_agg.pdf}
\caption{
Cloud occurrence by height calculated as the average of all voyages and stations
for the observed (OBS) and simulated lidar cloud mask. The total cloud fraction
(CF), average shortwave (SW) and longwave (LW) are shown in the legend. The
bands span the 16$^\mathrm{th}$--84$^\mathrm{th}$ percentile calculated from
the set of all voyages and stations. The subsets \textbf{(a--g)} are described
in the text (Section \ref{sec:results}).}
\label{fig:cloud-occurrence}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=\textwidth]{img/cl_agg.pdf}
\caption{
Cloud occurrence by height calculated as the average of all voyages and
stations for the observed (OBS) and simulated lidar cloud mask. The total cloud
fraction (CF), average shortwave (SW) and longwave (LW) are shown in the
legend, and the relative frequency of occurrence (RFO) of the subset. The bands
span the 16$^\mathrm{th}$--84$^\mathrm{th}$ percentile calculated from the set
of all voyages and stations. The subsets \textbf{(a--g)} are described in the
text (Section \ref{sec:results}).
}
\label{fig:cloud-occurrence}
\end{figure}
